### 2019-09-27 vesicle_code/docs/softmatter/permeableVes.tex
Working on soft matter TeX

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Problem formulation} \label{sc:formulate}
Consider a semi-permeable vesicle suspended in an unbounded viscous
fluid domain, subjected to an imposed flow $\mbu_\infty(\mbx)$, for any
$\mbx \in \RR^2$.  Assume that the interior and exterior fluids have the same viscosity $\mu$. Let $\mbx$ be the position of the interface $\gamma$, $\mbu$ the fluid velocity and $p$ the pressure. In the vanishing Reynolds number limit, the governing equations for the ambient fluid can be written as: 
%
\begin{subequations}
\begin{align}
-\nabla p + \mu \triangle \mbu = 0 \quad\text{in}\quad
  \RR^2\setminus\gamma  &  \\
% 
\nabla \cdot \mbu = 0  \quad\text{in}\quad \RR^2\setminus\gamma &\\
%
\mbu(\mbx) \rightarrow \mbu_\infty(\mbx) \quad \text{as} \quad  \norm{\mbx} \rightarrow \infty & 
 \end{align} \label{eqn:governing}
\end{subequations}%
%
The modified jump conditions in the case of a semi-permeable vesicle can
be summarized as follows.  Let $\mbn$ the outward normal to $\gamma$ and
$\jump{\cdot}$ denote the jump across the interface. The jump condition
for the hydrodynamic stress remains the same:
\begin{align} 
  \jump{\Sigma\cdot\mbn} = \mbf_\text{mem}, 
\end{align}
where $\Sigma$ is the hydrodynamic stress tensor. The fluid velocity is
continuous across the membrane i.e.,
\begin{align}
  \jump{\mbu} = 0. 
\end{align}
However, the kinematic condition is modified to account for the fact
that the fluid can move through the membrane. A standard choice appears
to be
%
\begin{align}
  \mbu - \dot{\mbx} = - \beta (\mbf_\text{mem} \cdot \mbn) \mbn
      \quad\text{on}\quad\gamma. 
\end{align}
%
Here, $\beta$ is a constant and the membrane force is the usual
sum of the bending and tension forces.

We can use the governing equations to write a differential equation for
the area of the vesicle as a function of time. The area inside a single
vesicle $\gamma$ parameterized with $\mbx$ is
\begin{align}
  A(t) = \frac{1}{2}\int_{\gamma} (\mbx \cdot \mbn)\, ds = 
    \frac{1}{2}\int_{0}^{2\pi} \left(\mbx \cdot
    \pderiv{\mbx}{\theta}^\perp\right)
    \, d\theta.
\end{align}
Taking the time derivative of $A(t)$,
\begin{align}
  \dot{A}(t) &= \frac{1}{2}\int_{0}^{2\pi} \left(\dot{\mbx} \cdot
  \pderiv{\mbx}{\theta}^{\perp} + 
    \mbx \cdot \pderiv{\dot{\mbx}}{\theta}^{\perp}\right) d\theta, \\
  %&= \frac{1}{2}
  %\int_{0}^{2\pi}(\dot{\mbx}\cdot\mbn)\left\|\pderiv{\mbx}{\theta}\right\|d\theta +
  %   \frac{1}{2}\int_{0}^{2\pi}
  %  \left(\mbx \cdot \pderiv{\dot{\mbx}}{\theta}^{\perp}\right)d\theta, \\
  %&= \frac{k_w}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds +
  %\frac{1}{2}\int_{0}^{2\pi}\left(\mbx \cdot \pderiv{}{t}\left(\mbn
  %\left\|\pderiv{\mbx}{\theta}\right\|\right)\right)d\theta, \\
  %&= \frac{k_w}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds + \frac{1}{2}
  %\int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right)ds + \frac{1}{2}\int_{0}^{2\pi}
  %\frac{\mbx\cdot\mbn}{\left\|\pderiv{\mbx}{\theta}\right\|}
  %\left(\pderiv{\mbx}{\theta}\cdot
  %\pderiv{\dot{\mbx}}{\theta}\right)d\theta \\
  &= \frac{k_w}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds + \frac{1}{2}
  \int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right)ds + \frac{1}{2}\int_{\gamma}
  (\mbx\cdot\mbn) (\mbx_s \cdot \dot{\mbx}_s)\, ds.
\end{align}
To satisfy the inextensibilty condition, $\mbx_s \cdot \dot{\mbx}_s = 0$, the time derivative of $A(t)$ is
\begin{align}
     \dot{A}(t) &= \frac{k_w}{2}
     \int_{\gamma}\left(\mbf\cdot\mbn\right)ds
     + \frac{1}{2} \int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right)ds.
\end{align}
%... 
%\begin{align}
%    \dot{A}(t) &= \frac{k_w}{2}
%    \int_{\gamma}\left(\mbf\cdot\mbn\right)ds+\frac{1}{2}\int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right) ds,
%\end{align}
which we re-write as
\begin{align}
    \dot{A}(t) &= \frac{k_w}{2}
    \int_{\gamma}\left(\mbf\cdot\mbn\right)ds-\frac{1}{2}\int_{\gamma}\left(\mbx^{\perp}\cdot\dot{\mbx}_s\right) ds.
\end{align}
Applying integration by parts and re-writing,
%\begin{align}
%    \dot{A}(t) &= \frac{k_w}{2}
%    \int_{\gamma}\left(\mbf\cdot\mbn\right)ds+\frac{1}{2}\int_{\gamma}\left(\mbx^{\perp}_s\cdot\dot{\mbx}\right) ds,
%\end{align}
%which we re-write as
\begin{align}
 %   \dot{A}(t) &= \frac{k_w}{2}
 %   \int_{\gamma}\left(\mbf\cdot\mbn\right)ds+\frac{1}{2}\int_{\gamma}\left(\dot{\mbx}\cdot\mbn\right),\\
    \dot{A}(t) &= k_w \int_{\gamma}\left(\mbf\cdot\mbn\right)ds.
\end{align}
At steady state,
\begin{align}
    \dot{A}(t) &= k_w \int_{\gamma}\left(\mbf\cdot\mbn\right)ds =0.
\end{align}
Replacing $\mbf$ with its relation, applying integration by parts twice and using Frenet-serret formulas,  
\begin{align}
k_w\int_{\gamma}\kappa_b\kappa^3 ds +k_w\int_{\gamma} \kappa\sigma ds  = 0. 
\end{align} 
%We now replace $\mbf$ with its relation
%\begin{align}
%   k_w\int_{\gamma}
%   \left((-\kappa_b\mbx_{ssss}+(\sigma\mbx_s)_s)\cdot\mbn\right)ds &=0.
%\end{align}
%Applying integration by parts,
%\begin{align}
%     k_w\int_{\gamma}\left(\kappa_b\mbx_{sss}-\sigma\mbx_s\right)\cdot
%     \mbn_s ds &=0.
%\end{align}
%From the Frenet-Serret formulas, we have 
%\begin{align}
%     -k_w\int_{\gamma}
%     \left(\kappa_b\mbx_{sss}-\sigma\mbx_s\right)\cdot\kappa\mbx_s ds &=0.
%\end{align}

%Applying integration by parts and Frenet-Serret again
%\begin{align}
%     k_w\int_{\gamma}
%     \kappa_b\kappa\left(\mbx_{ss}\cdot\mbx_{ss}\right)ds + k_w
%     \int_{\gamma} \kappa_b \kappa_s(\mbx_{ss} \cdot \mbx_s)ds +k_w\int_{\gamma}\kappa\sigma ds  &= 0,\\
%    k_w\int_{\gamma} \kappa_b\kappa(\kappa\mbn \cdot
%     \kappa\mbn)+ k_w \int_{\gamma} \kappa_b \kappa_s(\mbx_{ss} \cdot
%     \mbx_s)ds +k_w\int_{\gamma}\kappa\sigma ds &= 0,
%\end{align}
%which we re-write as
%\begin{align}
%   k_w\int_{\gamma}\kappa_b\kappa^3 ds + k_w \int_{\gamma} \kappa_b
%   \kappa_s(\mbx_{ss} \cdot \mbx_s)ds +k_w\int_{\gamma} \kappa\sigma ds = 0.
%\end{align}
%Applying Frenet-serret again,
%\begin{align}
%    k_w\int_{\gamma}\kappa_b\kappa^3 ds + k_w \int_{\gamma} \kappa_b
%    \kappa_s(\kappa\mbn \cdot \TT)ds +k_w\int_{\gamma} \kappa\sigma ds = 0, \\
%    k_w\int_{\gamma}\kappa_b\kappa^3 ds +k_w\int_{\gamma} \kappa\sigma ds  = 0, 
%\end{align}
%we compare this to our numerical results.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Integral equation formulation and non-dimensionalization}
There are multiple ways to convert the PDE problem into integral
equations. The coupled set of
integro-differential equations satisfy the given interfacial conditions:
\begin{align}
  \label{eqn:vesVelocity}
  \dot{\mbx} &= \mbu_\infty(\mbx) + k_w
  (RT\jump{c}+\mbf_\text{mem}\cdot\mbn)\mbn
  + \SS [\mbf_\text{mem}],  \\
  \mbx_s\cdot\dot{\mbx}_s &= 0 
\end{align}
This satisfies all the jump conditions. As usual, $\SS$ is the single
layer potential.  We introduce the notation
\begin{align}
  B[\mbx]\mbf &= -\kappa_b\frac{d^4}{ds^4} \mbf, \\
  T[\mbx]\sigma &= (\sigma \mbx_s)_s, \\
  P[\mbx]\mbf &= (\mbf \cdot \mbn) \mbn, \\
  D[\mbx]\mbf &= \mbx_s \cdot \mbf_s,
\end{align}
where $\mbn$ is the outward unit normal of the vesicle parameterized by
$\mbx$, and $d/ds$ is its arclength derivative.  Dropping the dependence
of the operators on $\mbx$, the dynamics of the vesicle are governed by
\begin{align}
  \dot{\mbx} &= \mbu_{\infty}(\mbx) + 
  k_wRT\jump{c}\mbn + k_wP(B\mbx + T\sigma) + \SS(B\mbx + T\sigma), \label{eq:full}\\
  D \dot{\mbx} &= 0.
\end{align}

Following the analysis of~\cite{vee-gue-zor-bir2009} and
disregarding background flow, we define scales of $\mbx$, $t$, $k_w$,
and $c$ to nondimensionalize equation (\ref{eq:full}) as follows. The
length is scaled using the radius of a circle with the same perimeter,
$L$, as the vesicle, $R_0 = \frac{L}{2\pi}$. From analysis, the time
scale $\tau$ is defined as $\tau = \frac{\mu R_0^2}{k_b}$, the tension
scale, $Q$, is defined as $Q = \frac{k_b}{R_0^2}$, the water flux scale,
$W$, is defined as $W=\frac{R_0}{\mu}$, and the concentration scale,
$C$, is defined as $C=\frac{k_b}{R_0^3RT}$. The governing equation in
nondimensional form is
\begin{align}
    \dot{\Tilde{\mbx}} =  \Tilde{k_w}\jump{\tilde{c}}\mbn +
    \Tilde{k_w}P\big(B[\Tilde{\mbx}]\Tilde{\mbx}+T[\Tilde{\mbx}]\Tilde{\sigma}\big)
    +\SS\big( B[\Tilde{\mbx}]\Tilde{\mbx} + T[\Tilde{\mbx}]\Tilde{\sigma}\big).
\end{align}
In our current implementation, we let $\jump{c} = 0$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical methods}
To address stiffness associated with high-order derivatives,
equation~\eqref{eqn:vesVelocity} is discretized with a semi-implicit
time stepping method similar to our previous works.  First, we introduce
the notation
\begin{align}
  B[\mbx]\mbf &= -\kappa_b\frac{d^4}{ds^4} \mbf, \\
  T[\mbx]\sigma &= (\sigma \mbx_s)_s, \\
  P[\mbx]\mbf &= (\mbf \cdot \mbn) \mbn, \\
  D[\mbx]\mbf &= \mbx_s \cdot \mbf_s,
\end{align}
where $\mbn$ is the outward unit normal of the vesicle
parameterized by $\mbx$, and $d/ds$ is its arclength derivative.
Dropping the dependence of the operators on $\mbx$, the dynamics of the
vesicle are governed by
\begin{align}
  \dot{\mbx} &= \mbu_{\infty}(\mbx) + 
  \beta P(B\mbx + T\sigma) + \sgl(B\mbx + T\sigma), \\
  D \dot{\mbx} &= 0.
\end{align}
Using the notation $B^N$ to denote the bending operator due to the
vesicle configuration at time $t_N$, and similar notation for the other
operators, we apply the semi-implicit time stepping method
\begin{align} 
\begin{split}
  \frac{\mbx^{N+1} - \mbx^N}{\Delta t} = \mbu_\infty(\mbx^N) 
  + \beta P^N(B^N\mbx^{N+1} + T^N\sigma^{N+1}) \\
   + \sgl^N(B^N\mbx^{N+1} + T^N\sigma^{N+1}).
   \end{split} 
\end{align}
Applying $D$ to the first-order time discretization of
equation~\eqref{eqn:vesVelocity}, the inextensibility condition is
\begin{align*}
  &D^N(\mbx^{N+1} - \mbx^N) = 0 \\ 
  \Rightarrow &D^N\mbx^{N+1} = D^N \mbx^N \\ 
  \Rightarrow &D^N\mbx^{N+1} = 1.
\end{align*}
Finally, we write the time stepping method in matrix form as
\begin{align}
  A \left(
    \begin{array}{c}
      \mbx^{N+1} \\ \sigma^{N+1}
    \end{array}
  \right) = 
  \left(
    \begin{array}{c}
      \mbx^{N} + \Delta t \mbu_\infty(\mbx^N) \\ \mathbf{1}
    \end{array}
  \right),
\end{align}
where
\begin{align}
 A = \left(
  \begin{array}{cc}
    I + \Delta t \beta P^N B^N + \Delta t \sgl^N B^N & 
    -\Delta t P^N T^N - \Delta t \sgl^N T^N \\
    D^N & 0
  \end{array}
  \right).
\end{align}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Problem formulation} \label{sc:formulate}
Consider a semi-permeable vesicle suspended in an unbounded viscous
fluid domain, subjected to an imposed flow $\mbu_\infty(\mbx)$, for any
$\mbx \in \RR^2$.  Assume that the interior and exterior fluids have the same viscosity $\mu$. Let $\mbx$ be the position of the interface $\gamma$, $\mbu$ the fluid velocity and $p$ the pressure. In the vanishing Reynolds number limit, the governing equations for the ambient fluid can be written as: 
%
\begin{subequations}
\begin{align}
-\nabla p + \mu \triangle \mbu = 0 \quad\text{in}\quad
  \RR^2\setminus\gamma  &  \\
% 
\nabla \cdot \mbu = 0  \quad\text{in}\quad \RR^2\setminus\gamma &\\
%
\mbu(\mbx) \rightarrow \mbu_\infty(\mbx) \quad \text{as} \quad  \norm{\mbx} \rightarrow \infty & 
 \end{align} \label{eqn:governing}
\end{subequations}
\begin{figure}[H]
	\centering
	\epsfig{file =figures/vesicleschem.pdf, width=.6\columnwidth}
	\caption{$\Omega$ is the unbounded fluid domain and $\gamma$ is the vesicle membrane. In addition to the vesicle-induced flow, a shear flow is imposed in the far field, $\mbu_\infty$.}
\end{figure}
The modified jump conditions in the case of a semi-permeable vesicle can
be summarized as follows.  Let $\mbn$ the outward normal to $\gamma$ and
$\jump{\cdot}$ denote the jump across the interface. The jump condition
for the hydrodynamic stress remains the same:
\begin{align} 
  \jump{\Sigma\cdot\mbn} = \mbf, 
\end{align}
where $\Sigma$ is the hydrodynamic stress tensor. The fluid velocity is
continuous across the membrane i.e.,
\begin{align}
  \jump{\mbu} = 0. 
\end{align}
However, the kinematic condition is modified to account for the fact
that the fluid can move through the membrane. A standard choice appears
to be
\begin{align}
  \mbu - \dot{\mbx} = - \beta (\text{RT}\jump{c}+\mbf \cdot \mbn) \mbn
      \quad\text{on}\quad\gamma. 
\end{align}
Here, $\beta$, R, and T are constants, $c$ is the solute concentration, and the membrane force is the usual sum of the bending and tension forces,
\begin{subequations}
	\begin{align}
	\mbf = \mbf_{\text{bending}}+\mbf_{\text{tension}},  &  \\
	% 
	\mbf_{\text{bending}} = -\kappa_b\mbx_{ssss}, &\\
	%
	\mbf_{\text{tension}} = (\sigma\mbx_s)_s. & 
	\end{align} \label{eqn:bendten}
\end{subequations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Integral equation formulation and non-dimensionalization}
There are multiple ways to convert the PDE problem into integral
equations. The coupled set of
integro-differential equations satisfy the given interfacial conditions:
\begin{align}
  \label{eqn:vesVelocity}
  \dot{\mbx} = \mbu_\infty(\mbx) + \beta
  (RT\jump{c}+\mbf\cdot\mbn)\mbn
  + \sgl [\mbf], & \\
  \mbx_s\cdot\dot{\mbx}_s = 0 &
\end{align}
This satisfies all the jump conditions. As usual, $\sgl$ is the single
layer potential.  We introduce the notation
\begin{align}
  B[\mbx]\mbf &= -\kappa_b\frac{d^4}{ds^4} \mbf, \\
  T[\mbx]\sigma &= (\sigma \mbx_s)_s, \\
  P[\mbx]\mbf &= (\mbf \cdot \mbn) \mbn, \\
  D[\mbx]\mbf &= \mbx_s \cdot \mbf_s,
\end{align}
where $\mbn$ is the outward unit normal of the vesicle parameterized by
$\mbx$, and $d/ds$ is its arclength derivative.  Dropping the dependence
of the operators on $\mbx$, the dynamics of the vesicle are governed by
\begin{align}
  \dot{\mbx} &= \mbu_{\infty}(\mbx) + 
  \beta RT\jump{c}\mbn + \beta P(B\mbx + T\sigma) + \sgl(B\mbx + T\sigma), \label{eq:full}\\
  D \dot{\mbx} &= 0.
\end{align}

Following the analysis of~\cite{vee-gue-zor-bir2009} and
disregarding background flow, we define scales of $\mbx$, $t$, $\beta$,
and $c$ to nondimensionalize equation (\ref{eq:full}) as follows. The
length is scaled using the radius of a circle with the same perimeter,
$L$, as the vesicle, $R_0 = \frac{L}{2\pi}$. From analysis, the time
scale $\tau$ is defined as $\tau = \frac{\mu R_0^2}{k_b}$, the tension
scale, $Q$, is defined as $Q = \frac{k_b}{R_0^2}$, the water flux scale,
$W$, is defined as $W=\frac{R_0}{\mu}$, and the concentration scale,
$C$, is defined as $C=\frac{k_b}{R_0^3RT}$. The governing equation in
nondimensional form is
\begin{align}
    \dot{\Tilde{\mbx}} = \Tilde{\mbu}_{\infty} + \Tilde{\beta}\jump{\tilde{c}}\mbn +
    \Tilde{\beta}P\big(B[\Tilde{\mbx}]\Tilde{\mbx}+T[\Tilde{\mbx}]\Tilde{\sigma}\big)
    +\sgl\big( B[\Tilde{\mbx}]\Tilde{\mbx} + T[\Tilde{\mbx}]\Tilde{\sigma}\big).
\end{align}
In our current implementation, we let $\jump{c} = 0$. The remaining equations are written in dimensionless form, unless stated otherwise, and for simplicity of notation we remove the tildes.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical methods}
To address stiffness associated with high-order derivatives,
equation~\eqref{eqn:vesVelocity} is discretized with a semi-implicit
time stepping method similar to our previous works.  
where $\mbn$ is the outward unit normal of the vesicle
parameterized by $\mbx$, and $d/ds$ is its arclength derivative.
Dropping the dependence of the operators on $\mbx$, the dynamics of the
vesicle are governed by
\begin{align}
  \dot{\mbx} &= \mbu_{\infty}(\mbx) + 
  \beta P(B\mbx + T\sigma) + \sgl(B\mbx + T\sigma), \\
  D \dot{\mbx} &= 0.
\end{align}
Using the notation $B^N$ to denote the bending operator due to the
vesicle configuration at time $t_N$, and similar notation for the other
operators, we apply the semi-implicit time stepping method
\begin{align} 
\begin{split}
  \frac{\mbx^{N+1} - \mbx^N}{\Delta t} = \mbu_\infty(\mbx^N) 
  + \beta P^N(B^N\mbx^{N+1} + T^N\sigma^{N+1}) \\
   + \sgl^N(B^N\mbx^{N+1} + T^N\sigma^{N+1}).
   \end{split} 
\end{align}
Applying $D$ to the first-order time discretization of
equation~\eqref{eqn:vesVelocity}, the inextensibility condition is
\begin{align*}
  &D^N(\mbx^{N+1} - \mbx^N) = 0 \\ 
  \Rightarrow &D^N\mbx^{N+1} = D^N \mbx^N \\ 
  \Rightarrow &D^N\mbx^{N+1} = 1.
\end{align*}
Finally, we write the time stepping method in matrix form as
\begin{align}
  A \left(
    \begin{array}{c}
      \mbx^{N+1} \\ \sigma^{N+1}
    \end{array}
  \right) = 
  \left(
    \begin{array}{c}
      \mbx^{N} + \Delta t \mbu_\infty(\mbx^N) \\ \mathbf{1}
    \end{array}
  \right),
\end{align}
where
\begin{align}
 A = \left(
  \begin{array}{cc}
    I + \Delta t \beta P^N B^N + \Delta t \sgl^N B^N & 
    -\Delta t P^N T^N - \Delta t \sgl^N T^N \\
    D^N & 0
  \end{array}
  \right).
\end{align}

Analytically, we use the governing equations to write a differential equation for
the area of the vesicle as a function of time. The area inside a single
vesicle $\gamma$ parameterized with $\mbx$ is
\begin{align}
A(t) = \frac{1}{2}\int_{\gamma} (\mbx \cdot \mbn)\, ds = 
\frac{1}{2}\int_{0}^{2\pi} \left(\mbx \cdot
\pderiv{\mbx}{\theta}^\perp\right)
\, d\theta.
\end{align}
Taking the time derivative of $A(t)$,
\begin{align}
\dot{A}(t) &= \frac{1}{2}\int_{0}^{2\pi} \left(\dot{\mbx} \cdot
\pderiv{\mbx}{\theta}^{\perp} + 
\mbx \cdot \pderiv{\dot{\mbx}}{\theta}^{\perp}\right) d\theta, \\
%&= \frac{1}{2}
%\int_{0}^{2\pi}(\dot{\mbx}\cdot\mbn)\left\|\pderiv{\mbx}{\theta}\right\|d\theta +
%   \frac{1}{2}\int_{0}^{2\pi}
%  \left(\mbx \cdot \pderiv{\dot{\mbx}}{\theta}^{\perp}\right)d\theta, \\
%&= \frac{\beta}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds +
%\frac{1}{2}\int_{0}^{2\pi}\left(\mbx \cdot \pderiv{}{t}\left(\mbn
%\left\|\pderiv{\mbx}{\theta}\right\|\right)\right)d\theta, \\
%&= \frac{\beta}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds + \frac{1}{2}
%\int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right)ds + \frac{1}{2}\int_{0}^{2\pi}
%\frac{\mbx\cdot\mbn}{\left\|\pderiv{\mbx}{\theta}\right\|}
%\left(\pderiv{\mbx}{\theta}\cdot
%\pderiv{\dot{\mbx}}{\theta}\right)d\theta \\
&= \frac{\beta}{2} \int_{\gamma}\left(\mbf\cdot\mbn\right)ds + \frac{1}{2}
\int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right)ds + \frac{1}{2}\int_{\gamma}
(\mbx\cdot\mbn) (\mbx_s \cdot \dot{\mbx}_s)\, ds.
\end{align}
To satisfy the inextensibilty condition, $\mbx_s \cdot \dot{\mbx}_s = 0$, the time derivative of $A(t)$ is
\begin{align}
\dot{A}(t) &= \frac{\beta}{2}
\int_{\gamma}\left(\mbf\cdot\mbn\right)ds
+ \frac{1}{2} \int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right)ds.
\end{align}
%... 
%\begin{align}
%    \dot{A}(t) &= \frac{\beta}{2}
%    \int_{\gamma}\left(\mbf\cdot\mbn\right)ds+\frac{1}{2}\int_{\gamma}\left(\mbx\cdot\dot{\mbn}\right) ds,
%\end{align}
which we re-write as
\begin{align}
\dot{A}(t) &= \frac{\beta}{2}
\int_{\gamma}\left(\mbf\cdot\mbn\right)ds-\frac{1}{2}\int_{\gamma}\left(\mbx^{\perp}\cdot\dot{\mbx}_s\right) ds.
\end{align}
Applying integration by parts and re-writing,
%\begin{align}
%    \dot{A}(t) &= \frac{\beta}{2}
%    \int_{\gamma}\left(\mbf\cdot\mbn\right)ds+\frac{1}{2}\int_{\gamma}\left(\mbx^{\perp}_s\cdot\dot{\mbx}\right) ds,
%\end{align}
%which we re-write as
\begin{align}
%   \dot{A}(t) &= \frac{\beta}{2}
%   \int_{\gamma}\left(\mbf\cdot\mbn\right)ds+\frac{1}{2}\int_{\gamma}\left(\dot{\mbx}\cdot\mbn\right),\\
\dot{A}(t) &= \beta \int_{\gamma}\left(\mbf\cdot\mbn\right)ds.
\end{align}
At steady state,
\begin{align}
\dot{A}(t) &= \beta \int_{\gamma}\left(\mbf\cdot\mbn\right)ds =0.
\end{align}
Replacing $\mbf$ with its relation, applying integration by parts twice and using Frenet-serret formulas,  
\begin{align}
\beta\int_{\gamma}\kappa_b\kappa^3 ds +\beta\int_{\gamma} \kappa\sigma ds  = 0. 
\end{align} 
%We now replace $\mbf$ with its relation
%\begin{align}
%   \beta\int_{\gamma}
%   \left((-\kappa_b\mbx_{ssss}+(\sigma\mbx_s)_s)\cdot\mbn\right)ds &=0.
%\end{align}
%Applying integration by parts,
%\begin{align}
%     \beta\int_{\gamma}\left(\kappa_b\mbx_{sss}-\sigma\mbx_s\right)\cdot
%     \mbn_s ds &=0.
%\end{align}
%From the Frenet-Serret formulas, we have 
%\begin{align}
%     -\beta\int_{\gamma}
%     \left(\kappa_b\mbx_{sss}-\sigma\mbx_s\right)\cdot\kappa\mbx_s ds &=0.
%\end{align}

%Applying integration by parts and Frenet-Serret again
%\begin{align}
%     \beta\int_{\gamma}
%     \kappa_b\kappa\left(\mbx_{ss}\cdot\mbx_{ss}\right)ds + \beta
%     \int_{\gamma} \kappa_b \kappa_s(\mbx_{ss} \cdot \mbx_s)ds +\beta\int_{\gamma}\kappa\sigma ds  &= 0,\\
%    \beta\int_{\gamma} \kappa_b\kappa(\kappa\mbn \cdot
%     \kappa\mbn)+ \beta \int_{\gamma} \kappa_b \kappa_s(\mbx_{ss} \cdot
%     \mbx_s)ds +\beta\int_{\gamma}\kappa\sigma ds &= 0,
%\end{align}
%which we re-write as
%\begin{align}
%   \beta\int_{\gamma}\kappa_b\kappa^3 ds + \beta \int_{\gamma} \kappa_b
%   \kappa_s(\mbx_{ss} \cdot \mbx_s)ds +\beta\int_{\gamma} \kappa\sigma ds = 0.
%\end{align}
%Applying Frenet-serret again,
%\begin{align}
%    \beta\int_{\gamma}\kappa_b\kappa^3 ds + \beta \int_{\gamma} \kappa_b
%    \kappa_s(\kappa\mbn \cdot \TT)ds +\beta\int_{\gamma} \kappa\sigma ds = 0, \\
%    \beta\int_{\gamma}\kappa_b\kappa^3 ds +\beta\int_{\gamma} \kappa\sigma ds  = 0, 
%\end{align}
%we compare this to our numerical results.
